Commutative character sheaves and geometric types for supercuspidal representations

### 2017-08-31 CJM/second letter to CJM.tex
Added Prop to second letter to CJM

In addition to making changes prompted by the referee's comments, we have corrected an error pointed out to us in an e-mail from Will Savin.  Namely, we assumed incorrectly at the beginning of Section 3 that any character on $G(k)$ would vanish on $G\der(k)$.  Every character vanishes on $G(k)\der$, but in general these two groups are not the same (for example, if $G = \SL_2$ over $\FFF$ or $\PGL_2$ over a finite field of odd characteristic).  We adjusted the exposition in the introduction and beginning of Section 3 to correct this mistake, and added hypotheses in the statements of Corollary 3.8, Thereom 3.12 and Theorem 5.2.  We also added Section 4, where we describe some approaches for geometrizing characters that do not vanish on $G\der(k)$.

>>>>

In addition to making changes prompted by the referee's comments, we have corrected an error pointed out to us in an e-mail from Will Savin.  Namely, we assumed incorrectly at the beginning of Section 3 that any character on $G(k)$ would vanish on $G\der(k)$.  Every character vanishes on $G(k)\der$, but in general these two groups are not the same (for example, if $G = \SL_2$ over $\FFF$ or $\PGL_2$ over a finite field of odd characteristic).  We adjusted the exposition in the introduction and beginning of Section 3 to correct this mistake, and added hypotheses in the statements of Corollary 3.8, Thereom 3.12, Proposition 5.1 and Theorem 5.2.  We also added Section 4, where we describe some approaches for geometrizing characters that do not vanish on $G\der(k)$.
